QPLIB: A Library of Quadratic Programming Instances

### 2016-07-27 QPLIB-2.3.tex
typos corrected and Mosek added

Local search methods typically require as an input a solution $x'$ and attempt to improve it---either towards feasibility, or towards optimality, or both---using only information that is available in a neighborhood of $x'$. In general, local search methods are incomplete. As remarked above, however, local search methods deployed on a convex problem behave like complete methods, possibly via devices that that allow to find a feasible starting solution if there is one (the so-called ``phase 0'').

@@

The solvers in Table \ref{t:solvers} BB type methods are:
%
\begin{itemize}
 \item {\sc Antigone}, {\sc Baron}, {\sc Couenne}, {\sc Lindo}, {\sc LindoGlobal}, {\sc SCIP}, {\sc lgo\_bb}, which implement complete BB algorithms for QGQ;
 %
\item {\sc CPLEX}, which implements a complete BB algorithm for QGL;
%
 \item {\sc KNitro\_bb}, {\sc BonMin}, {\sc sBB}, {\sc XPress}, {\sc GuRoBi}, which implement complete BB algorithms for CGC. {\bf how about {\sc mosek}?}
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for QGQ. We also remark that CPLEX can currently only target problems with linear constraints when the objective function is nonconvex \cite{bliek}.

>>>>

Local search methods typically require as an input a solution $x'$ and attempt to improve it---either towards feasibility, or towards optimality, or both---using only information that is available in a neighborhood of $x'$. In general, local search methods are incomplete. As remarked above, however, local search methods deployed on a convex problem behave like complete methods, possibly via devices that that allow one to find a feasible starting solution if there is one (the so-called ``phase 0'').

@@

The solvers in Table \ref{t:solvers} BB type methods are:
%
\begin{itemize}
 \item {\sc Antigone}, {\sc Baron}, {\sc Couenne}, {\sc Lindo}, {\sc LindoGlobal}, {\sc SCIP}, {\sc lgo\_bb}, which implement complete BB algorithms for QGQ;
 %
\item {\sc CPLEX}, which implements a complete BB algorithm for QGL;
%
 \item {\sc Knitro\_bb}, {\sc BonMin}, {\sc sBB}, {\sc Xpress}, {\sc Gurobi}, and {\sc Mosek} which implement complete BB algorithms for CGC.}
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for QGQ. We also remark that CPLEX can currently only target problems with linear constraints when the objective function is nonconvex \cite{bliek}.
